Run-Time Monitoring with Adjustable Overheads Using Dataflow-Guided Filtering

### 2014-09-12 introduction.tex
a quick pass on the abstract and the intro

Previous studies have explored various design points in terms of efficiency,
flexibility, and hardware costs for implementing run-time monitors. Custom
hardware designs that target a single or narrow-range of monitors have been
shown to have low performance overheads. On the other hand, flexible systems
that support a range of monitors have shown much higher overheads. In this
paper, we explore a new trade-off dimension for run-time monitoring designs. We
propose to enable low overhead monitors without sacrificing flexibility by
using partial monitoring. This instead allows a trade-off between overheads and
monitoring coverage or accuracy.

Although partial monitoring comes at the cost of reduced monitoring coverage (i.e.,
effectiveness), this can still be very useful.
For example, partial
monitoring can enable a level of protection even for systems where the full
monitoring overheads are too high. This is especially true for energy- or
power-constrained systems or soft real-time systems where the monitoring
overhead should not exceed energy/power limits or real-time deadlines.
Additionally, partial monitoring can be used for debugging purposes
especially in the context of sampling-based or cooperative debugging techniques
which expect low coverage per run but use a large number of runs and users to
collect debugging information~\cite{liblit-pldi05, chilimbi-asplos04,
greathouse-cgo11}.

@@

% Filtering
Recent studies have shown that filtering out monitoring checks on clean or null
metadata can be used to reduce the overheads of monitoring \cite{fade-hpca14}.
For example, for an array bounds check, checking non-pointer accesses is
unnecessary. In addition to enabling partial monitoring, we show how a simple
extension to our dataflow engine enables this null metadata filtering.

The main contributions of this paper are summarized as follows:
\begin{itemize}
  \item We present a hardware architecture using a dataflow tracking engine to
  efficiently enable partial monitoring while preventing false positives. This
  hardware architecture is designed to be generally applicable to a wide-range
  of run-time monitoring techniques.
  \item We investigate interesting trade-offs in deciding what to skip for
  partial monitoring on the proposed architecture.
  \item We extend the dataflow engine to enable filtering null metadata to
  reduce overheads.
\end{itemize}

@@

% Evaluation
In order to evaluate our approach, we applied it to 4 different monitoring
techniques. These monitoring techniques vary in what events they monitor, the
size and semantics of their metadata, and the operations performed on metadata.
% Our experiments show that filtering reduces the average overhead of these
% monitors from 7-18x down to 13-300\%.
% In addition, with partial monitoring, for the monitoring schemes which still
% see average overheads of 300\%, we show that with just 10\% overheads, we can still
% provide 32-82\% of coverage on average. By increasing the
% overhead budget, this coverage rate can be increased. 
These monitors show baseline overheads of 4-16x without null metadata filtering
and 1.1-4.3x after null metadata filtering.  Our results show that with 1.5x
overhead, coverage of 43-82\% on average can still be achieved and that
overhead and coverage can be varied to create a trade-off.

% Section summary
This paper is organized as follows. Section~\ref{sec:monitoring} presents the
baseline parallel run-time monitoring model that this paper assumes.
Section~\ref{sec:dropping} discusses enabling partial monitoring using our dataflow tracking engine.
Section~\ref{sec:policies}
investigates the design space for dropping decisions for partial monitoring.
Section~\ref{sec:evaluation} presents our evaluation methodology and
results. Finally, we discuss related work in Section~\ref{sec:related} and
conclude in Section~\ref{sec:conclusion}.

>>>>

Previous studies have explored various design points in terms of efficiency,
flexibility, and hardware costs for implementing run-time monitors. Custom
hardware designs that target a single or narrow-range of monitors have been
shown to have low performance overheads. On the other hand, flexible systems
that support a range of monitors have shown much higher overheads. In this
paper, we explore a new trade-off dimension for run-time monitor designs. We
propose to enable low overhead monitors without sacrificing flexibility by
using partial monitoring. In essence, this enables a trade-off between overheads and
monitoring coverage or accuracy.

Although partial monitoring comes at the cost of reduced monitoring coverage (i.e.,
effectiveness), this can still be useful in many scenarios.
For example, partial
monitoring can enable a level of protection even for systems where the full
monitoring overheads are too high. This is especially true for energy- or
power-constrained systems or soft real-time systems where the monitoring
overhead should not exceed energy/power limits or real-time deadlines.
Additionally, partial monitoring can be used for debugging purposes
especially in the context of sampling-based or cooperative debugging techniques
which expect low coverage per run but use a large number of runs and users to
collect debugging information~\cite{liblit-pldi05, chilimbi-asplos04,
greathouse-cgo11}.

@@

% Filtering
Recent studies have shown that filtering out monitoring operations on clean or null
metadata can be used to reduce the overheads of monitoring \cite{fade-hpca14}.
For example, for an array bounds check, checking non-pointer accesses is
unnecessary. In addition to enabling partial monitoring, we show how a simple
extension to our dataflow engine enables this null metadata filtering.

The main contributions of this paper are summarized as follows:
\begin{itemize}
  \item We present a hardware architecture using a dataflow tracking engine to
  efficiently enable partial monitoring while preventing false positives. This
  hardware architecture is designed to be generally applicable to a wide-range
  of run-time monitoring techniques.
  \item We investigate multiple policies on when and which operations to drop 
  for partial monitoring, and show the trade-offs in the design space.
  \item We extend the dataflow engine to enable filtering null metadata to
  reduce overheads.
\end{itemize}

@@

% Evaluation
In order to evaluate our approach, we applied it to 4 different monitoring
techniques. These monitoring techniques vary in what events they monitor, the
size and semantics of their metadata, and the operations performed on metadata.
% Our experiments show that filtering reduces the average overhead of these
% monitors from 7-18x down to 13-300\%.
% In addition, with partial monitoring, for the monitoring schemes which still
% see average overheads of 300\%, we show that with just 10\% overheads, we can still
% provide 32-82\% of coverage on average. By increasing the
% overhead budget, this coverage rate can be increased. 
These monitors show slowdowns of 1.1-4.3x with the null metadata filtering when
implemented on a multi-core platform.
%4-16x without null metadata filtering
%and 1.1-4.3x after null metadata filtering.  
Our results show that the partial monitoring can still achieve coverage of 43-82\%
on average at the reduced slowdown of 1.5x. 
The results also show that overhead and coverage can be varied to create a trade-off.

% Section summary
This paper is organized as follows. Section~\ref{sec:monitoring} introduces the notion
of adjustable run-time monitoring with partial monitoring.
Section~\ref{sec:dropping} discusses the hardware architecture that enables 
partial monitoring using our dataflow tracking engine.
Section~\ref{sec:policies}
investigates the design space for dropping policies that determine when and which
monitoring operations to drop.
Section~\ref{sec:evaluation} presents our evaluation methodology and
results. Finally, we discuss related work in Section~\ref{sec:related} and
conclude in Section~\ref{sec:conclusion}.

### 2014-09-12 title.tex
a quick pass on the abstract and the intro

Recent studies have proposed various parallel run-time monitoring techniques to
improve the reliability, security, and debugging capabilities of computer
systems. However, these run-time monitors can introduce large performance and energy
overheads, especially when performed on programmable cores.
%Traditionally, these overheads have been an
%all-or-nothing cost; monitoring cannot be used if the overheads are considered
%too large.  
In this paper, we introduce a hardware dataflow tracking engine that enables
adjustable overheads through partial monitoring. This allows a trade-off to be
made between monitoring coverage and overhead. We show how this dataflow engine
can be extended to filter out monitoring operations associated with null
metadata in order to reduce overheads.
% In this paper, we introduce a hardware dataflow tracking engine that can be
% used to filter out unnecessary monitoring and enable adjustable partial monitoring.
% The dataflow engine can identify events with null metadata so that they can
% be filtered out. To further reduce the overhead of monitoring, we propose
% to enable a trade-off between monitoring coverage and overhead by dropping certain
% monitoring operations. For this partial monitoring, the dataflow engine is used
% to track dropped monitoring flows so that false positives can be avoided.
Given this architecture, we also investigate how the dropping decisions should be
made for partial monitoring and show that there exists a trade-off between closely
matching an overhead target and the coverage that can be achieved.
Our experimental results show that overheads can be reduced from 4-16x on
average to 1.5x while still achieving 43-82\% coverage.

>>>>

Recent studies have proposed various parallel run-time monitoring techniques to
improve the reliability, security, and debugging capabilities of computer
systems. However, these run-time monitors can introduce large performance and energy
overheads, especially when performed on programmable cores.
%Traditionally, these overheads have been an
%all-or-nothing cost; monitoring cannot be used if the overheads are considered
%too large.  
In this paper, we introduce a hardware dataflow tracking engine that enables
adjustable overheads through partial monitoring. This allows a trade-off to be
made between monitoring coverage and overhead. This dataflow engine
can also be extended to filter out monitoring operations associated with null
metadata in order to reduce overheads.
% In this paper, we introduce a hardware dataflow tracking engine that can be
% used to filter out unnecessary monitoring and enable adjustable partial monitoring.
% The dataflow engine can identify events with null metadata so that they can
% be filtered out. To further reduce the overhead of monitoring, we propose
% to enable a trade-off between monitoring coverage and overhead by dropping certain
% monitoring operations. For this partial monitoring, the dataflow engine is used
% to track dropped monitoring flows so that false positives can be avoided.
Given this architecture, we investigate how the dropping decisions should be
made for partial monitoring and show that there exists a trade-off between closely
matching an overhead target and the coverage that can be achieved.
Our experimental results show that overheads can be reduced significantly 
by trading off coverage. For example, the proposed architecture can still
achieve 43-82\% coverage when the slowdown is reduced from 1.1-4.3x to 1.5x.
\Ed{It's a bit strange to say reduced from 1.1x to 1.5x. Revise?}
